How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-01 tse-paper/content.tex
Improve number style
address my todos

To answer this question, we start our investigation---pictured in
\Cref{fig:overview}---with an
extensive literature survey (step 1).
The survey identifies various strategies to
analyze build logs, among which are developing
custom parsers, using regular expressions, doing manual inspections,
searching for keywords, or performing natural language processing.
However, there is currently no guidance on when to use which of these
approaches.
Unfortunately, our survey also shows that
less than half of the 61 works which rely on build log analysis
describe it in sufficient detail and that
the few available implementations are all based on either a custom parser
or regular expressions.
These two approaches are problematic, as their creation
and maintenance is manual and expensive, does not generalize across build
% TODO Discuss/Moritz: should we say 'our' experience? or
% 'one authors'?
% the latter might be too cumbersome
% Moritz: I have added a link to the disqus site of TT
% (where this originates from and would leave it in the
% current state)? Ok with you?
logs from different build tools, and is prone to errors,
as the experience of
TravisTorrent has shown~\cite{beller2017travistorrent,travistorrentquestions}.
In fact, some even ``strongly discourage'' the creation of such
parsers~\cite{urli2018design}.
In summary, the outcome of our literature survey shows the need for a new
generation of automated techniques to analyze build logs, which are
openly available and documented in detail, together with
guidance on when to use which technique.

@@

First, we filtered articles based on (a) their title and (b) the
contextual information Google Scholar displayed on its search results
page.
We included works at large that seemed to bear a resemblance to software
engineering and building software.
Following Kitchenham's protocol~\cite{kitchenham2009systematic},
we excluded
works written in a language unintelligible to the authors
(i.e., not English or German), which disregarded fewer than 1\% of search
hits.
% 'four' not clear and it gets lost that there are multiple search queries
% therefore I'll cut this part completely
% We then unified
% the results of the four search queries based on the link as the
% identifying element, removing 60 articles that appeared in more than
% one search query.
We removed duplicates based on the title and were
left with 256 articles (16\% of the original search results).

With these 256 remaining articles, we followed a backward snowball
sampling for related work.
If an article referenced a new work in the context
of build log analysis, we added the new one to the literature set.
This added five articles (eight before
duplicate elimination), leading to a total of 261
works.

@@

% TODO Caro: check article vs work occurrences, balance use
Third, since we had been careful to include rather than exclude borderline
works, a deeper evaluation excluded another 15 articles from the 87
works left after the second filter phase.
Multiple articles were extensions of others.
Of these, we only considered the earliest article which reported on
the analyzing of build logs.
This excluded another 11 articles.
In sum, we classified 61 articles in detail.

\subsection{Literature Classification}
Having trimmed down the set of articles by 95\%, we investigated the
remaining ones in-depth.
Our aim is to characterize how researchers work with build logs.

@@

To support the data extraction we created a template which we filled out
for each of the 61 works.
The template contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in detail?'' and
``What is the source of the build logs?''.
As recommended by Petersen et
al.~\cite{petersen2015guidelines}, we started the mapping survey with a
pilot:
both authors extracted data from the same five articles and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 56 articles evenly between the two authors
and inspected each article as closely as necessary to fill out the
template
with confidence,
starting from occurrences of ``log'' or ``build'' within the article's
text.

For questions that did not require a boolean answer, we allowed assigning
multiple tags or categories as the first part (``preparation phase'')
of a virtual open card sorting~\cite{zimmermann2016card}.
An example of this is the question ``What is the source of the build
log?'',
where we assigned tags such as ``Travis CI,''
``Industrial,'' ``Google,'' or
``self-built.''
Once we had classified all works, we went into the second phase of
card sorting
(``execution phase''), in which we grouped tags
together and found synonyms.
% the following adds to the example but is maybe unneeded / too much
For instance, in the case of the build log source we grouped
``Travis'' and ``Travis CI'' together and assigned ``Industrial'' to
all articles that used build logs provided by a company.
The replication package contains the data extraction template and all
results of this step~\cite{brandt2020chunk-replication}.

@@

\Cref{fig:failure-reason-PBE} depicts the year of appearance of these works. Although we applied no filtering by year in our initial search queries (see \Cref{sec:litsel}), the earliest work in our literature corpus stems only from 2001. There are various scattered works in the years between then and 2016, when the field of build log analysis started to grow rapidly.

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/years.pdf}
		\caption{Number of works analyzing build logs per year.}
		\label{fig:failure-reason-PBE}
\end{figure}

@@

\caption{Multi-label categorization of the 61 relevant articles.}
\label{fig:litsur_r}
\end{figure}

In this section, we describe what sort of information the articles in
our survey usually retrieved from build logs.
\Cref{fig:litsur_r} depicts these results.

\Cref{fig:litsur:info_target} gives an overview over the frequency of
the targeted information.
The precise information targeted in the build logs varied from article
to article, with a relatively long tail.
Most prominent was the search for errors (39\%), followed by extracting
the executed or the failing
tests (both 11\%).
There were also numerous works which targeted more specialized
information, such as the environments used during the
build~\cite{zolfagharinia2017not}, packages
installed~\cite{selberg2012use}, or hints to source files which
relate to build failures~\cite{ren2018automated}.

@@

\Cref{fig:litsur:use} shows the reason for the
investigated articles to analyze build logs, and the result also explains
the prevalence of classification.
The majority of articles (46\%) used the outcome of their build log
analysis to drive further research---and it is science aims to try to
classify and abstract.
Seo et al.~\cite{seo2014programmers}, for example,
categorized the types of compile errors encountered at
Google.
Other articles (10\%) used the gained insights to give feedback to
developers.
For 8\% of the articles the retrieved information was the input
to a next automatic onward processing step:
articles chose
tests that should be part of a reduced but still effective test
suite~\cite{shi2018evaluating} or filled a data structure with
build information, an information source for further tools aiming
to fix a failing build~\cite{vassallo2018un-break}.

@@

Of the 61 articles we inspected, 43 mentioned how they analyzed
build logs.
However, only 16 of these described their technique in detail.
We summarize the techniques that the articles
described for analyzing build logs in \Cref{tab:litsur:techniques}.

The most mentioned technique (34\%) was using a parser, where we also
included
rather imprecise statements like ``we parse the build
logs''~\cite{rahman2018impact}.
For such imprecise statements it was often not clear if they describe
a complex parser (including a tokenizer, lexer, etc.) or refer to a
simpler parsing tool based on regular expressions.
If we saw evidence for the latter, we assigned the tag
``Regular Expression'' instead of the tag ``Parser.''
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They started with a manual categorization of build logs and selected
search strings that identify the target category.
Based on the search strings they created a script that automatically
classifies the remaining logs.
Another 8\% of the investigated articles
employed machine learning such as natural language
processing or information retrieval techniques.
The rather general tags ``analysis'' and ``scan'' in
\Cref{tab:litsur:techniques}, stem---similar to the imprecise
statements about parsing---from the
words authors used to describe their techniques.
%such as
%``automatically analyzed [the build logs]''.

Only 25\% of the articles claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an updated version of them~\cite{rott2019empirische,
shi2018evaluating}, two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
and
another two
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao}.

\subsubsection{Which kinds of build logs are subject to
  analysis? (RQ 1.3)}
As the structure of build logs can change greatly depending on the
build tools contributing to it~\cite{staahl2014modeling},
we were interested in which (variety) build tools are
investigate in literature.
\Cref{fig:litsur:log_producer} shows the distribution of
build tools whose logs were analyzed by the articles in our survey.
Of the articles, 30\% analyzed
Maven~\cite{maven2019website},
16\% analyzed Gradle~\cite{gradle2020website},
and 10\% analyzed Ant build logs~\cite{ant2020website}.

A large fraction of the articles analyze build logs
from a small number of build tools.
In most cases, this is because the format of build logs
changes and
therefore ``parsers must be specialized to each build and test
framework''~\cite{tomassi2019bugswarm}.
Sometimes, aspects separate from the build log analysis motivate
the limitation to a specific build tool.
For example, Shi et al.
focussed on Maven
build logs because they also chose the PIT tool~\cite{coles2016pit}
to calculate coverage
and mutation score~\cite{shi2018evaluating}.
PIT is only available as a Maven plugin.
Only 7\% of the proposed techniques claimed to be
build tool-agnostic, while
several described they are covering multiple source build tools.
The majority of articles (42\%) analyzed logs produced by a build tool
that no second article supported.

In 38\% of cases, the articles collected build logs from Travis
CI~\cite{travisci2019webpage};
18\% of the articles processed logs from TravisTorrent; and 8\% included
build logs from industrial projects.
The number of logs analyzed varied greatly between the articles
and we were not always able to
extract it confidently.

23 of the articles analyzed more than a thousand build logs, while one
investigated up to 122 million logs.
Of the surveyed articles, 31\% claim to have published their data to
enable further research.
However, we found no clear reuse of build log data sets with the
exception of TravisTorrent~\cite{beller2017travistorrent}, which
Vassallo et al.~\cite{vassallo2017a-tale},
Ghaleb et al.~\cite{ghaleb2019studying},
and several other articles studied.

@@

% ----- descriptive / general -----
Our literature survey shows that despite its relatively young age
(first mentioned in a paper in 2001, vast majority after
2016), \textbf{build log analysis is an established technique}
in the literature, with 61 articles making use of it.

@@

% ----- technique RQ 1.2 -----
\textbf{Most log analysis is automated.} Automated approaches are
necessary as many studies target a large number of builds.
Articles
that explicitly mention a manual analysis of the logs, mostly
restrict their work to few logs or take a ``representative sample to
make manual analysis feasible''~\cite{zolfagharinia2017not}.
We observed \textbf{very little reuse of build log analysis tools},
even though articles reported that
\textbf{developing automated analysis tools requires a lot of effort}.
Urli et al.~\cite{urli2018design} strongly discouraged from parsing
build logs for information as it is ``too error prone,'' while other
articles pointed to the effort of developing a custom tool.
Regular expressions are known to be tedious to
maintain~\cite{michael2019regexes}.
% not sure if we can state that (no data on this, more 'impression')
In addition, we rarely saw articles justifying why they use a certain
technique to analyze build logs as there is a general \textbf{lack of
guidance on when to use which technique}.

% ----- kinds of build logs RQ1.3 -----
Several articles noted the variety in log formats for different build
tools, which requires customizing build log techniques for
every supported build tool.
% The following two sentences are passive, however flipped around
% have a different meaning (we want build tool -> study count)
\Cref{fig:litsur:log_producer} shows that only a few distinct
build tools are the target of
many studies and tools (roughly, area A).
The majority of build tools was however only targeted by one
article each (roughly, area B).
From this we follow that the large tail of
\textbf{seldomly-investigated
environments would benefit from the
existence of a more generic solution.}
% In most cases, \textbf{researchers analyze build logs from open
% source projects}, obtained through Travis CI.
% In addition, we saw several articles that targeted the logs of only
% one specific software project.

@@

% TODO Moritz: is this okay (here)?
% maybe it's better to add it to Threats to Validity with the heading:
% \texbf{Modifying the Build Process.}
% Moritz: I think best to decided once we read the paper
% top to bottom. For now, it seems ok

@@

We designed and implemented three chunk retrieval
techniques based on approaches
previously described by several articles:
\emph{Program Synthesis by Example (PBE)}
mimics regular expressions, while simplifying
their development.
From the field of information retrieval, we leverage a
\emph{Common Text Similarity (CTS)} approach
and implement the ad hoc approach of
searching for specific strings as \emph{Keyword Search (KWS)}.

@@

\subsection{Common Text Similarity (CTS)}
Text Similarity approaches are widely used to filter unstructured
textual software artifacts~\cite{runeson2007detection,
marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
These approaches fall into the broader area of information retrieval
techniques, which several of the articles from our literature survey
used to analyze build logs.
Similar to these approaches, we designed a chunk retrieval
technique that
retrieves those lines from a build log which are most
similar to examples given by the user.

@@

\Cref{lst:chunk-example} shows two excerpts
from Android build logs.
When we train PBE with these two examples, it produces
a regular expression program similar to the one presented in
\Cref{lst:prose-program-simplified}.
The retrieval
starts after a colon and a line separator and before a capital
letter.
It ends before two line separators,
which is consistent with the two example
chunks from \Cref{lst:chunk-example}.
This shows that the characters structuring the text around the chunk are
crucial for regular expressions to identify a log chunk.
In fact, if we add the third example from \Cref{lst:chunk-example-3}
to the training set (which has a
different structural representation),
PBE is not able to synthesize a program anymore and returns
``\texttt{no program found}.''
We later express this difference in structural representation through
separating log chunks into \emph{structural categories}.
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a
\emph{different structural category}.
% TODO Moritz: is this fitting here?
% or too much 'foreshadowing' too far down in the hierarchy
% Would recommend to delete -- it simply follows later
The results of the empirical comparison study on the chunk retrieval
techniques
show that the structural representation of the targeted chunk greatly
influences
the performance of the chunk retrieval techniques.

@@

In the literature survey we saw that few articles justify why they
use a certain build log analysis technique and concluded that there
is a lack of guidance on when to use which technique.
% add (see \Cref{sec:lit-sur:discussion}) ?
To address this lack of guidance we conduct an empirical study
comparing the three novel chunk retrieval techniques we presented in
\Cref{sec:techniques}.
We vary the conditions under which we train and run the techniques
to answer when a technique performs best and which conditions should
influence the choice for one technique over the others.

@@

For each build log, we manually marked
the chunk that describes why the build
failed---the information targeted by most of the articles in our
literature survey.
To be able to configure the keyword search technique,
the data set associates each chunk with keywords that we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
If the chunks were surrounded by the same markings
within the log, we assigned them the \emph{same structural category},
as described in \Cref{sec:crt-example}.

@@

The goal of this paper is to support practitioners and researchers in
their decision on how to analyze build logs.
To this end, we
conducted a systematic mapping survey to map out the available build
log analysis techniques.
We saw that, while build log analysis is widely used, it is often
a side part of an article and implementations are rarely reused.
This shows the need for a new generation of generic and automated
build log analysis techniques that need little effort to set up.

>>>>

To answer this question, we start our investigation---pictured in
\Cref{fig:overview}---with an
extensive literature survey (step 1).
The survey identifies various strategies to
analyze build logs, among which are developing
custom parsers, using regular expressions, doing manual inspections,
searching for keywords, or performing natural language processing.
However, there is currently no guidance on when to use which of these
approaches.
Unfortunately, our survey also shows that
less than half of the 61 works which rely on build log analysis
describe it in sufficient detail and that
the few available implementations are all based on either a custom parser
or regular expressions.
These two approaches are problematic, as their creation
and maintenance is manual and expensive, does not generalize across build
logs from different build tools, and is prone to errors,
as the experience of
TravisTorrent has
shown~\cite{beller2017travistorrent,travistorrentquestions}.
In fact, some even ``strongly discourage'' the creation of such
parsers~\cite{urli2018design}.
In summary, the outcome of our literature survey shows the need for a new
generation of automated techniques to analyze build logs, which are
openly available and documented in detail, together with
guidance on when to use which technique.

@@

First, we filtered works based on (a) their title and (b) the
contextual information Google Scholar displayed on its search results
page.
We included works at large that seemed to bear a resemblance to software
engineering and building software.
Following Kitchenham's protocol~\cite{kitchenham2009systematic},
we excluded
works written in a language unintelligible to the authors
(i.e., not English or German), which disregarded fewer than 1\% of search
hits.
% 'four' not clear and it gets lost that there are multiple search queries
% therefore I'll cut this part completely:
% We then unified
% the results of the four search queries based on the link as the
% identifying element, removing 60 works that appeared in more than
% one search query.
We removed duplicates based on the title and were
left with 256 works (16\% of the original search results).

With these 256 remaining works, we followed a backward snowball
sampling for related work.
If a work referenced a new work in the context
of build log analysis, we added the new one to the literature set.
This added five works (eight before
duplicate elimination), leading to a total of 261
works.

@@

Third, since we had been careful to include rather than exclude borderline
works, a deeper evaluation excluded another 15 works from the 87
works left after the second filter phase.
Multiple works were extensions of others.
Of these, we only considered the earliest work which reported on
the analyzing of build logs.
This excluded another 11 works.
In sum, we classified 61 works in detail.

\subsection{Literature Classification}
Having trimmed down the set of works by 95\%, we investigated the
remaining ones in-depth.
Our aim is to characterize how researchers work with build logs.

@@

To support the data extraction we created a template which we filled out
for each of the 61 works.
The template contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in detail?'' and
``What is the source of the build logs?''.
As recommended by Petersen et
al.~\cite{petersen2015guidelines}, we started the mapping survey with a
pilot:
both authors extracted data from the same five works and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 56 works evenly between the two authors
and inspected each works as closely as necessary to fill out the
template
with confidence,
starting from occurrences of ``log'' or ``build'' within the works's
text.

For questions that did not require a boolean answer, we allowed assigning
multiple tags or categories as the first part (``preparation phase'')
of a virtual open card sorting~\cite{zimmermann2016card}.
An example of this is the question ``What is the source of the build
log?'',
where we assigned tags such as ``Travis CI,''
``Industrial,'' ``Google,'' or
``self-built.''
Once we had classified all works, we went into the second phase of
card sorting
(``execution phase''), in which we grouped tags
together and found synonyms.
% the following adds to the example but is maybe unneeded / too much
For instance, in the case of the build log source we grouped
``Travis'' and ``Travis CI'' together and assigned ``Industrial'' to
all works that used build logs provided by a company.
The replication package contains the data extraction template and all
results of this step~\cite{brandt2020chunk-replication}.

@@

\Cref{fig:lit-years} depicts the year of appearance of these
works.
Although we applied no filtering by year in our initial search queries
(see \Cref{sec:litsel}), the earliest work in our literature corpus
stems only from 2001.
There are various scattered works in the years between then and 2016,
when the field of build log analysis started to grow rapidly.

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/years.pdf}
		\caption{Number of works analyzing build logs per year.}
		\label{fig:lit-years}
\end{figure}

@@

\caption{Multi-label categorization of the 61 relevant works.}
\label{fig:litsur_r}
\end{figure}

In this section, we describe what sort of information the works in
our survey usually retrieved from build logs.
\Cref{fig:litsur_r} depicts these results.

\Cref{fig:litsur:info_target} gives an overview over the frequency of
the targeted information.
The precise information targeted in the build logs varied from work
to work, with a relatively long tail.
Most prominent was the search for errors (39\%), followed by extracting
the executed or the failing
tests (both 11\%).
There were also numerous works which targeted more specialized
information, such as the environments used during the
build~\cite{zolfagharinia2017not}, packages
installed~\cite{selberg2012use}, or hints to source files which
relate to build failures~\cite{ren2018automated}.

@@

\Cref{fig:litsur:use} shows the reason for the
investigated works to analyze build logs, and the result also explains
the prevalence of classification.
The majority of works (46\%) used the outcome of their build log
analysis to drive further research---and it is science aims to try to
classify and abstract.
Seo et al.~\cite{seo2014programmers}, for example,
categorized the types of compile errors encountered at
Google.
Other works (10\%) used the gained insights to give feedback to
developers.
For 8\% of the works the retrieved information was the input
to a next automatic onward processing step:
works chose
tests that should be part of a reduced but still effective test
suite~\cite{shi2018evaluating} or filled a data structure with
build information, an information source for further tools aiming
to fix a failing build~\cite{vassallo2018un-break}.

@@

Of the 61 works we inspected, 43 mentioned how they analyzed
build logs.
However, only 16 of these described their technique in detail.
We summarize the techniques that the works
described for analyzing build logs in \Cref{tab:litsur:techniques}.

The most mentioned technique (34\%) was using a parser, where we also
included
rather imprecise statements like ``we parse the build
logs''~\cite{rahman2018impact}.
For such imprecise statements it was often not clear if they describe
a complex parser (including a tokenizer, lexer, etc.) or refer to a
simpler parsing tool based on regular expressions.
If we saw evidence for the latter, we assigned the tag
``Regular Expression'' instead of the tag ``Parser.''
25\% of the works described the use of regular expressions and 20\%
inspected the logs manually.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They started with a manual categorization of build logs and selected
search strings that identify the target category.
Based on the search strings they created a script that automatically
classifies the remaining logs.
Another 8\% of the investigated works
employed machine learning such as natural language
processing or information retrieval techniques.
The rather general tags ``analysis'' and ``scan'' in
\Cref{tab:litsur:techniques}, stem---similar to the imprecise
statements about parsing---from the
words authors used to describe their techniques.
%such as
%``automatically analyzed [the build logs]''.

Only 25\% of the works claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
Five works employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an updated version of them~\cite{rott2019empirische,
shi2018evaluating}, two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
and
another two
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao}.

\subsubsection{Which kinds of build logs are subject to
  analysis? (RQ 1.3)}
As the structure of build logs can change greatly depending on the
build tools contributing to it~\cite{staahl2014modeling},
we were interested in which (variety) build tools are
investigate in literature.
\Cref{fig:litsur:log_producer} shows the distribution of
build tools whose logs were analyzed by the works in our survey.
Of the works, 30\% analyzed
Maven~\cite{maven2019website},
16\% analyzed Gradle~\cite{gradle2020website},
and 10\% analyzed Ant build logs~\cite{ant2020website}.

A large fraction of the works analyze build logs
from a small number of build tools.
In most cases, this is because the format of build logs
changes and
therefore ``parsers must be specialized to each build and test
framework''~\cite{tomassi2019bugswarm}.
Sometimes, aspects separate from the build log analysis motivate
the limitation to a specific build tool.
For example, Shi et al.
focussed on Maven
build logs because they also chose the PIT tool~\cite{coles2016pit}
to calculate coverage
and mutation score~\cite{shi2018evaluating}.
PIT is only available as a Maven plugin.
Only 7\% of the proposed techniques claimed to be
build tool-agnostic, while
several described they are covering multiple source build tools.
The majority of works (42\%) analyzed logs produced by a build tool
that no second work investigated.

In 38\% of cases, the works collected build logs from Travis
CI~\cite{travisci2019webpage};
18\% of the works analyzed logs from TravisTorrent; and 8\% included
build logs from industrial projects.
The number of logs analyzed varied greatly between the works
and we were not always able to
extract it confidently.

23 of the works analyzed more than a thousand build logs, while one
investigated up to 122 million logs.
Of the surveyed works, 31\% claim to have published their data to
enable further research.
However, we found no clear reuse of build log data sets with the
exception of TravisTorrent~\cite{beller2017travistorrent}, which
Vassallo et al.~\cite{vassallo2017a-tale},
Ghaleb et al.~\cite{ghaleb2019studying},
and several other works studied.

@@

% ----- descriptive / general -----
Our literature survey shows that despite its relatively young age
(first mentioned in a paper in 2001, vast majority after
2016), \textbf{build log analysis is an established technique}
in the literature, with 61 works making use of it.

@@

% ----- technique RQ 1.2 -----
\textbf{Most log analysis is automated.} Automated approaches are
necessary as many studies target a large number of builds.
works
that explicitly mention a manual analysis of the logs, mostly
restrict their work to few logs or take a ``representative sample to
make manual analysis feasible''~\cite{zolfagharinia2017not}.
We observed \textbf{very little reuse of build log analysis tools},
even though works reported that
\textbf{developing automated analysis tools requires a lot of effort}.
Urli et al.~\cite{urli2018design} strongly discouraged from parsing
build logs for information as it is ``too error prone,'' while other
works pointed to the effort of developing a custom tool.
Regular expressions are known to be tedious to
maintain~\cite{michael2019regexes}.
% not sure if we can state that (no data on this, more 'impression')
In addition, we rarely saw works justifying why they use a certain
technique to analyze build logs as there is a general \textbf{lack of
guidance on when to use which technique}.

% ----- kinds of build logs RQ1.3 -----
Several works noted the variety in log formats for different build
tools, which requires customizing build log techniques for
every supported build tool.
% The following two sentences are passive, however flipped around
% have a different meaning (we want build tool -> study count)
\Cref{fig:litsur:log_producer} shows that only a few distinct
build tools are the target of
many studies and tools (roughly, area A).
The majority of build tools was however only targeted by one
work each (roughly, area B).
From this we follow that the large tail of
\textbf{seldomly-investigated
environments would benefit from the
existence of a more generic solution.}
% In most cases, \textbf{researchers analyze build logs from open
% source projects}, obtained through Travis CI.
% In addition, we saw several works that targeted the logs of only
% one specific software project.

@@

% TODO Moritz: is this okay (here)?
% maybe it's better to add it to Threats to Validity with the heading:
% \texbf{Modifying the Build Process.}
% Moritz: I think best to decided once we read the paper
% top to bottom.
%For now, it seems ok

@@

We designed and implemented three chunk retrieval
techniques based on approaches
previously described by several works:
\emph{Program Synthesis by Example (PBE)}
mimics regular expressions, while simplifying
their development.
From the field of information retrieval, we leverage a
\emph{Common Text Similarity (CTS)} approach
and implement the ad hoc approach of
searching for specific strings as \emph{Keyword Search (KWS)}.

@@

\subsection{Common Text Similarity (CTS)}
Text Similarity approaches are widely used to filter unstructured
textual software artifacts~\cite{runeson2007detection,
marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
These approaches fall into the broader area of information retrieval
techniques, which several of the works from our literature survey
used to analyze build logs.
Similar to these approaches, we designed a chunk retrieval
technique that
retrieves those lines from a build log which are most
similar to examples given by the user.

@@

\Cref{lst:chunk-example} shows two excerpts
from Android build logs.
When we train PBE with these two examples, it produces
a regular expression program similar to the one presented in
\Cref{lst:prose-program-simplified}.
The retrieval
starts after a colon and a line separator and before a capital
letter.
It ends before two line separators,
which is consistent with the two example
chunks from \Cref{lst:chunk-example}.
This shows that the characters structuring the text around the chunk are
crucial for regular expressions to identify a log chunk.
In fact, if we add the third example from \Cref{lst:chunk-example-3}
to the training set (which has a
different structural representation),
PBE is not able to synthesize a program anymore and returns
``\texttt{no program found}.''
We later express this difference in structural representation through
separating log chunks into \emph{structural categories}.
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a
\emph{different structural category}.

@@

In the literature survey we saw that few works justify why they
use a certain build log analysis technique and concluded that there
is a lack of guidance on when to use which technique.
% add (see \Cref{sec:lit-sur:discussion}) ?
To address this lack of guidance we conduct an empirical study
comparing the three novel chunk retrieval techniques we presented in
\Cref{sec:techniques}.
We vary the conditions under which we train and run the techniques
to answer when a technique performs best and which conditions should
influence the choice for one technique over the others.

@@

For each build log, we manually marked
the chunk that describes why the build
failed---the information targeted by most of the works in our
literature survey.
To be able to configure the keyword search technique,
the data set associates each chunk with keywords that we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
If the chunks were surrounded by the same markings
within the log, we assigned them the \emph{same structural category},
as described in \Cref{sec:crt-example}.

@@

The goal of this paper is to support practitioners and researchers in
their decision on how to analyze build logs.
To this end, we
conducted a systematic mapping survey to map out the available build
log analysis techniques.
We saw that, while build log analysis is widely used, it is often
a side part of an work and implementations are rarely reused.
This shows the need for a new generation of generic and automated
build log analysis techniques that need little effort to set up.
